---
title: "rsa_group_stats_10_24_18"
author: "WBR"
date: "10/24/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# knitr::opts_chunk$set(out.width = "70%")
```

## Load and prepare data 

```{r}
# RSA sum stats
library(tidyverse)
library(afex)
library(ggforce)

# same verb RSA even for random
rsa.SVDP = read.table("/Users/wbr/walter/fmri/sms_scan_analyses/rsa_singletrial/singletrial_4_rsatoolbox/november_17/RSAmeans_same_verb_10_23_18.txt", header = TRUE, stringsAsFactors = TRUE)

rsa.SVDP$condition = ifelse(rsa.SVDP$condition == "random", "r_sameverb",ifelse(rsa.SVDP$condition == "intact","intact","scrambled")) 
rsa.SVDP = rsa.SVDP %>% filter(condition == "r_sameverb")

# SVSS with positions and beta threshold
rsa.SVSS = read.table("/Users/wbr/walter/fmri/sms_scan_analyses/rsa_singletrial/singletrial_4_rsatoolbox/november_17/RSAmeans_same_position_10_23_18.txt", header = TRUE, stringsAsFactors = TRUE)


# add random r_sameverb for one combined dataset
rsa = bind_rows(rsa.SVDP, rsa.SVSS)

# noisiest subject
bad_subs = c('s001', "s008","s016", "s027","s043","s032","s039","s041")
rsa$drop_subs = rsa$sub %in% bad_subs
rsa = rsa[!(rsa$drop_subs == TRUE),]
       
rsa.sumstats = rsa %>% group_by(roi, condition) %>% summarise(mean = mean(similarity), sd = sd(similarity))


# the rois
PM_rois = c('near-phc-ant-L', 'near-phc-ant-R', 'lh-ANG', 'rh-ANG', 'lh-PCC', 'rh-PCC',	'lh-Prec',	'rh-Prec', 'lh-RSC', 'rh-RSC')
AT_rois = c('near-prc-L',	'near-prc-R', 	'lh-TPole', 	'rh-TPole', 'lh-OFC', 'rh-OFC')
HIPP_rois = c('near-hipp-body-L',	'near-hipp-body-R',	'near-hipp-head-L',	'near-hipp-head-R')
PM_HIPP_rois = c('near-hipp-body-L',	'near-hipp-body-R',	'near-hipp-head-L',	'near-hipp-head-R', 
                 'near-phc-ant-L', 'near-phc-ant-R', 'lh-ANG', 'rh-ANG', 'lh-PCC', 'rh-PCC',	'lh-Prec',	'rh-Prec', 'lh-RSC', 'rh-RSC')
IFG_INS = c('lh-insula-short', 'lh-insula-inf', 'lh-inf-opercular', 'lh-inf-triang', 'rh-insula-short', 'rh-insula-inf', 'rh-inf-opercular', 'rh-inf-triang')

# vmpfc = c('near-VMPFC') 

# make networks factor
# first make logical vectors for member regions
rsa$PM = rsa$roi %in% PM_rois
rsa$AT = rsa$roi %in% AT_rois
rsa$HIPP = rsa$roi %in% HIPP_rois
rsa$PM_HIPP = rsa$roi %in% PM_HIPP_rois
rsa$IFG_INS = rsa$roi %in% IFG_INS

# now assign group label in single column
# rsa$roi_group = ifelse(rsa$PM == TRUE, "PM", ifelse(rsa$AT == TRUE, "AT", ifelse(rsa$HIPP == TRUE,"HIPP", "Other" )))
rsa$roi_group = ifelse(rsa$PM == TRUE, "PM", ifelse(rsa$AT == TRUE, "AT", ifelse(rsa$HIPP == TRUE,"HIPP", ifelse(rsa$IFG_INS == TRUE, "IFG_INS","Other"))))
# delete the logical vectors
rsa[,6:11] = NULL
# make group a factor
rsa$roi_group = as.factor(rsa$roi_group)

# wish I did this earlier but hindsight yada yada
rsa$roi = gsub(".*body-L$", "lh-hipp-body", rsa$roi)
rsa$roi = gsub(".*body-R$", "rh-hipp-body", rsa$roi)
rsa$roi = gsub(".*head-L$", "lh-hipp-head", rsa$roi)
rsa$roi = gsub(".*head-R$", "rh-hipp-head", rsa$roi)
rsa$roi = gsub(".*ant-L$", "lh-phc-ant", rsa$roi)
rsa$roi = gsub(".*ant-R$", "rh-phc-ant", rsa$roi)
# rsa$roi = gsub(".*VMPFC", "VMPFC", rsa$roi)
rsa$roi = gsub(".*prc-L$", "lh-prc", rsa$roi)
rsa$roi = gsub(".*prc-R$", "rh-prc", rsa$roi)
########################
# PMAT AT and HIPP only
rsa.PMAT = rsa %>% filter(roi_group != "Other") %>% filter(roi_group != "IFG_INS")
```

## Plot by network cluster

```{r fig.width = 12, fig.asp = .62}
clust.fig.dat = rsa.PMAT %>% group_by(sub,condition,roi_group) %>% summarise(similarity = mean(similarity))
clusters.rois = ggplot(data = clust.fig.dat, aes(x = factor(condition), y = similarity))  + geom_boxplot(outlier.shape = NA)  +  facet_wrap( ~roi_group) + scale_y_continuous(limits = c(-.05, .35))
clusters.rois = clusters.rois + ylab("Similarity") + theme(text = element_text(size = 30, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -90,hjust = 0)) + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled"))
clusters.rois
```

## Full within subject network*condition ANOVA with follow-up holm-corrected paired contrasts

```{r}
m1 = aov_ez("sub", "similarity", rsa.PMAT, within = c("condition", "roi_group"))
m1
ls.m1 = lsmeans(m1,~condition|roi_group,contr = "pairwise", adjust = NULL)
ls.m1
contrast(ls.m1, alpha=0.05, method="pairwise", adjust= "holm")
```

## Make roi groups

```{r}
rsa.PM = rsa %>% filter(roi_group == "PM")
rsa.AT = rsa %>% filter(roi_group == "AT")
rsa.HIPP = rsa %>% filter(roi_group == "HIPP")
```

## Separate network plots

```{r fig.width = 12, fig.asp = .62}

pm.fig.dat = rsa.PMAT %>%  filter(roi_group == "PM") %>% group_by(sub,condition) %>% summarise(similarity = mean(similarity))
PM.check = ggplot(data = pm.fig.dat, aes(x = factor(condition), y = similarity))  + geom_boxplot(outlier.shape = NA) + scale_y_continuous(limits = c(-.05, .3))
PM.check = PM.check + ylab("Similarity") + theme(text = element_text(size = 30, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -45,hjust = 0)) + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled")) 
PM.check
# ggsave("pm.all.pdf", plot = last_plot(), dpi = 600 )

at.fig.dat = rsa.PMAT %>%  filter(roi_group == "AT") %>% group_by(sub,condition) %>% summarise(similarity = mean(similarity))
AT.check = ggplot(data = at.fig.dat, aes(x = factor(condition), y = similarity))  + geom_boxplot(outlier.shape = NA) + scale_y_continuous(limits = c(-.1, .3))
AT.check = AT.check + ylab("Similarity") + theme(text = element_text(size = 30, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -45,hjust = 0)) + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled"))
AT.check
# ggsave("at.all.pdf", plot = last_plot(), dpi = 600 )

#HIPP
hipp.fig.dat = rsa.PMAT %>%  filter(roi_group == "HIPP") %>% group_by(sub,condition) %>% summarise(similarity = mean(similarity))
hipp.check = ggplot(data = hipp.fig.dat, aes(x = factor(condition), y = similarity))  + geom_boxplot(outlier.shape = NA) + scale_y_continuous(limits = c(-.05, .17))
hipp.check = hipp.check + ylab("Similarity") + theme(text = element_text(size = 30, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -45,hjust = 0)) + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled"))
hipp.check
# ggsave("at.all.pdf", plot = last_plot(), dpi = 600 )

```

## Which PM ROIs drive effects
# Earlier observed that r_sameverb differeed from all other conditions in PM network 
# ROI*condition ANOVA indicated significant main effects of condition and roi, and a trending interaction
# Follow up contrasts indicate that r_sameverb is significantly different from at least one other condition in:
# lh-ANG,rh-ANG,lh-PCC,lh-Prec,rh-Prec
# Next will plot rh-Prec as representative region


```{r}
m1.PM = aov_ez("sub", "similarity", rsa.PM, within = c("condition", "roi"))
m1.PM
ls.PM = lsmeans(m1.PM,~condition|roi,contr = "pairwise", adjust = NULL)
# ls.PM
contrast(ls.PM, alpha=0.05, method="pairwise", adjust= "holm")
```

## Plot example region
# rh-Prec
roi = rh.Prec:
 contrast                    estimate        SE     df t.ratio p.value
 r_sameverb - intact    -7.448388e-02 0.0202036 334.82  -3.687  0.0013
 r_sameverb - random    -1.105341e-01 0.0202036 334.82  -5.471  <.0001
 r_sameverb - scrambled -4.931024e-02 0.0202036 334.82  -2.441  0.0455
 intact - random        -3.605024e-02 0.0202036 334.82  -1.784  0.1505
 intact - scrambled      2.517365e-02 0.0202036 334.82   1.246  0.2136
 random - scrambled      6.122388e-02 0.0202036 334.82   3.030  0.0105
 
```{r}
pm.fig.dat = rsa %>%  filter(roi == "rh-Prec") %>% group_by(sub,condition) %>% summarise(similarity = mean(similarity))
PM.check = ggplot(data = pm.fig.dat, aes(x = factor(condition), y = similarity))  + geom_boxplot(outlier.shape = NA) + scale_y_continuous(limits = c(-.05, .3))
PM.check = PM.check + ylab("Similarity") + theme(text = element_text(size = 30, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -45,hjust = 0)) + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled")) 
PM.check
# ggsave("pm.all.pdf", plot = last_plot(), dpi = 600 )



# rsa.PM.example = rsa %>% filter(roi == "rh-Prec")
# PM.plot = ggplot(data = rsa.PM.example, aes(x = factor(condition), y = similarity)) + geom_boxplot(outlier.shape = NA) + theme(text = element_text(size = 25, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -45,hjust = 0))
# PM.plot = PM.plot + ylab("Similarity") + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled"))
# PM.plot
# ggsave("rh-prec.pdf", plot = last_plot(), dpi = 600 )
```

## Which AT ROIs drive effects
# Earlier we saw that intact and r_sameverb are different in AT (p = .03) and intact and scrambled are different (p = .04)
# Which ROIs drive that effect? Curiously this second ANOVA is trending for a main effect of condition...?
# Effect is driven by prc with, r-prc trending for difference between intact and r_samverb (p = .09) and intact and scrambled (p = .09)

```{r}
m1.AT = aov_ez("sub", "similarity", rsa.AT, within = c("condition", "roi"))
m1.AT
ls.AT = lsmeans(m1.AT,~condition|roi,contr = "pairwise", adjust = NULL)
# ls.AT
contrast(ls.AT, alpha=0.05, method="pairwise", adjust= "holm")
```

## Plot AT example region: r-prc
roi = rh.prc:
 contrast                   estimate         SE     df t.ratio p.value
 r_sameverb - intact    -0.046949294 0.01899278 147.74  -2.472  0.0874
 r_sameverb - random    -0.008561882 0.01899278 147.74  -0.451  1.0000
 r_sameverb - scrambled -0.001848824 0.01899278 147.74  -0.097  1.0000
 intact - random         0.038387412 0.01899278 147.74   2.021  0.1803
 intact - scrambled      0.045100471 0.01899278 147.74   2.375  0.0943
 random - scrambled      0.006713059 0.01899278 147.74   0.353  1.0000

```{r}
at.fig.dat = rsa %>%  filter(roi == "rh-prc") %>% group_by(sub,condition) %>% summarise(similarity = mean(similarity))
at.check = ggplot(data = at.fig.dat, aes(x = factor(condition), y = similarity))  + geom_boxplot(outlier.shape = NA) + scale_y_continuous(limits = c(-.1, .3))
at.check = at.check + ylab("Similarity") + theme(text = element_text(size = 30, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -45,hjust = 0)) + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled")) 
at.check
# ggsave("pm.all.pdf", plot = last_plot(), dpi = 600 )


# rsa.AT.example = rsa %>% filter(roi == "rh-prc")
# AT.plot = ggplot(data = rsa.AT.example, aes(x = factor(condition), y = similarity)) + geom_boxplot(outlier.shape = NA) + theme(text = element_text(size = 25, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -45,hjust = 0))
# AT.plot = AT.plot + ylab("Similarity") + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled"))
# AT.plot
```

## Which ROIs in HIPP are doing anything
# lh-hipp-body has trending effect between intact and same-verb (p = .09)

```{r}
m1.HIPP = aov_ez("sub", "similarity", rsa.HIPP, within = c("condition","roi"))
m1.HIPP
ls.HIPP = lsmeans(m1.HIPP,~condition,contr = "pairwise", adjust = NULL)
# ls.HIPP
contrast(ls.HIPP, alpha=0.05, method="pairwise", adjust= "holm")
```

## plot left hipp body

```{r}
rsa.HIPP.example = rsa %>% filter(roi == "lh-hipp-head") %>% group_by(sub,condition) %>% summarise(similarity = mean(similarity))
HIPP.plot = ggplot(data = rsa.HIPP.example, aes(x = factor(condition), y = similarity)) + geom_boxplot(outlier.shape = NA) + theme(text = element_text(size = 25, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -45,hjust = 0))
HIPP.plot = HIPP.plot + ylab("Similarity") + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled"))
HIPP.plot
```

```{r}
rsa.VMPFC = rsa %>% filter(roi == "VMPFC") %>% group_by(sub,condition) %>% summarise(similarity = mean(similarity))
VMPFC.plot = ggplot(data = rsa.VMPFC, aes(x = factor(condition), y = similarity)) + geom_boxplot(outlier.shape = NA) + theme(text = element_text(size = 25, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -45,hjust = 0))
VMPFC.plot = VMPFC.plot + ylab("Similarity") + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled"))
VMPFC.plot
```



## VMPFC, nada yet

```{r}
rsa.VMPFC = rsa %>% filter(roi == "VMPFC")
m1.VMPFC = aov_ez("sub", "similarity", rsa.VMPFC, within = c("condition"))
m1.VMPFC
ls.VMPFC = lsmeans(m1.VMPFC,~condition,contr = "pairwise", adjust = NULL)
ls.VMPFC
contrast(ls.VMPFC, alpha=0.05, method="pairwise", adjust= "holm")
```

```{r fig.width = 12, fig.asp = .62}

pm.fig.dat = rsa.PMAT %>%  filter(roi_group == "PM") %>% group_by(sub,roi,condition) %>% summarise(similarity = mean(similarity))
PM.check = ggplot(data = pm.fig.dat, aes(x = factor(condition), y = similarity))  + geom_boxplot(outlier.shape = NA) + scale_y_continuous(limits = c(-.05, .3)) +  facet_wrap( ~roi, ncol=5)
PM.check = PM.check + ylab("Similarity") + theme(text = element_text(size = 30, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -45,hjust = 0)) + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled")) 
PM.check
```

```{r fig.width = 12, fig.asp = .62}

multi.fig.dat = rsa %>% group_by(sub,roi,condition) %>% summarise(similarity = mean(similarity))

for (ipage in 1:12) {
  ggplot(data = multi.fig.dat, aes(x = factor(condition), y = similarity)) + scale_y_continuous(limits = c(-.05, .3)) + geom_boxplot() + facet_wrap_paginate(~roi, nrow=2, ncol=2, page=ipage) + theme(text = element_text(size = 30, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -45,hjust = 0)) + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled"))
  fname = sprintf("otherrois_10_24_18_%d.pdf", ipage) 
  ggsave(fname)
}
```

```{r}
rsa.IFG = rsa %>% filter(roi_group == "IFG_INS")
m1.IFG = aov_ez("sub", "similarity", rsa.IFG, within = c("condition", "roi"))
m1.IFG
ls.IFG = lsmeans(m1.IFG,~condition|roi,contr = "pairwise", adjust = NULL)
# ls.IFG
contrast(ls.IFG, alpha=0.05, method="pairwise", adjust= "holm")
```

```{r fig.width = 12, fig.asp = .62}

pm.fig.dat = rsa.IFG %>% group_by(sub,roi,condition) %>% summarise(similarity = mean(similarity))
PM.check = ggplot(data = pm.fig.dat, aes(x = factor(condition), y = similarity))  + geom_boxplot() + scale_y_continuous(limits = c(-.05, .3)) +  facet_wrap( ~roi, ncol=5)
PM.check = PM.check + ylab("Similarity") + theme(text = element_text(size = 30, face = "bold"),axis.title.x=element_blank(),axis.text.x=element_text(angle = -45,hjust = 0)) + scale_x_discrete(labels = c("Intact", "Same Verb","Same Position","Scrambled")) 
PM.check
```

```{r}
# is anything sig dif with intact besides same position??
# rsa$sub = factor(rsa$sub)
# rsa.all = rsa %>% filter(rsa$position == 1)  
# rsa.all = rsa.all %>% filter(rsa$sub != "s041")
# rsa.all = rsa.all %>%   group_by(sub,roi,condition) %>% summarise(similarity =mean(similarity))
# rsa.all = rsa %>% filter(rsa$roi != "lh-occ-pole")
m1.all = aov_ez("sub", "similarity", rsa, within = c("condition", "roi"))
m1.all
ls.all = lsmeans(m1.all,~condition|roi,contr = "pairwise", adjust = NULL)
# ls.IFG
contrast(ls.all, alpha=0.05, method="pairwise", adjust= "holm")
```

```{r}
rsa.mpfc = rsa %>% filter(rsa$roi == "lh-MPFC" )
rsa.mpfc = rsa.mpfc %>% group_by(sub,roi,condition) %>% summarise(similarity = mean(similarity))
m1.all = aov_ez("sub", "similarity", rsa.mpfc, within = c("condition"))
m1.all
ls.all = lsmeans(m1.all,~condition,contr = "pairwise", adjust = NULL)
ls.all
contrast(ls.all, alpha=0.05, method="pairwise", adjust= "holm")
```


```{r}
rsa.mpfc = rsa %>% filter(rsa$roi == "near-hipp-tail-L" )
rsa.mpfc = rsa.mpfc %>% group_by(sub,roi,condition) %>% summarise(similarity = mean(similarity))
m1.all = aov_ez("sub", "similarity", rsa.mpfc, within = c("condition"))
m1.all
ls.all = lsmeans(m1.all,~condition,contr = "pairwise", adjust = NULL)
ls.all
contrast(ls.all, alpha=0.05, method="pairwise", adjust= "holm")
```

















